---
title: "Gov 51 PS2"
format: pdf
editor: visual
---

## Gov 51 PS 2

Github Repository: <https://github.com/meganmartinez-25/Gov51-PS2.git>

```{r}
#Initial Push Command 
library(tidyverse)
gay<-read.csv("data/raw/gay.csv")
gay_reshaped <- read.csv("data/raw/gayreshaped.csv")
ccap_2012 <-read.csv("data/raw/ccap2012.csv")

gay




```

Question 1:

```{r}
nrow(gay)
head(gay)

gay

```

P1: There are 69592 observations.

P2: ##!! Confused by the Question: How many unique values does study take?

P3: The treatment conditions are "No Contact," "Recycling Script by Gay Canvassers," "Same-Sex Marriage Script by Gay Canvassers, "Recycling Script by Straight Canvassers," and "Same-Sex Marriage Script by Straight Canvassers."

Q1.2 :

```{r}
gay_updated <- gay |> 
  filter(study == 1, wave ==1 ) |> 
  group_by(treatment) |> 
  summarize(mean_ssm = mean(ssm, na.rm = TRUE), 
            sd_ssm = sd(ssm, na.rm = TRUE))

gay_updated

names(gay)

```

Q1.2 Recycling Script by Gay Canvasser was the treatment with the highest ssm of 3.13.

Q1.3: Yes, the standard deviations are about the same as one another, which is important for a randomized sample because this means that there is not much variation between the groups, otherwise, if there is a standard deviation higher than the others, then there would likely be outliers impacting a group, and therefore, it would be difficult to say that each group would be an accurate comparison of one another.

Q1.4- Data Table and Bar Graph

```{r}
gay_stats <- gay_updated |> 
  knitr::kable(caption = "Summary Statistics for Gay Sample by Treatment",
               format = "latex", 
               booktabs = TRUE,
               digits = 2)
               
gay_updatedstats



gay_updatedRE <- gay_updated %>% 
  mutate(treatment = case_when(
    treatment == "No Contact" ~ "NO", 
    treatment == "Recycling Script by Gay Canvasser" ~ "Rec-Gay",
    treatment == "Same-Sex Marriage Script by Gay Canvasser" ~ "Same-Gay",
    treatment == "Recycling Script by Straight Canvasser" ~ "Rec-Strt", 
    treatment == "Same-Sex Marriage Script by Straight Canvasser" ~ "Same-Strt"))

gay_plot <- ggplot(gay_updatedRE, aes(x = treatment, y =`mean_ssm`)) +
  geom_col()+ 
  coord_cartesian(ylim = c(0,5))+
  labs(x = "Treatment Groups",
       y = "Means of Same-Sex Marriage Attitudes ",
       title = "Mean of Same-Sex Marriage Attitudes for Different Treatment Groups ")

gay_plot



  
```

1.2

```{r}

gay_updated <- gay |> 
  filter(study == 1, wave ==1 ) |> 
  group_by(treatment) |> 
  summarize(mean_ssm = mean(ssm, na.rm = TRUE), 
            sd_ssm = sd(ssm, na.rm = TRUE))

mean_Gay <- gay_updated |> 
  filter(treatment == "Same-Sex Marriage Script by Gay Canvasser") |> 
  pull(mean_ssm)
  
mean_NO <- gay_updated |> 
  filter(treatment == "No Contact") |> 
  pull(mean_ssm)

sd_Gay <- gay_updated |> 
  filter(treatment == "Same-Sex Marriage Script by Gay Canvasser") |> 
  pull(sd_ssm)
  
sd_NO <- gay_updated |> 
  filter(treatment == "No Contact") |> 
  pull(sd_ssm)

gay_updated 

stan_diff <- (mean_Gay - mean_NO) / (((sd_Gay + sd_NO)^(1/2))/2)

stan_diff



```

Yes, the standardized difference in absolute values is .192075, which is less than .25. This untilimately means that there is a good balance between the groups, and at their baseline they are similar.

Q1.6 (do we want only diff in means not standardized)?

```{r}

gay_updated2 <- gay |> 
  filter(study == 1, wave ==2 ) |> 
  group_by(treatment) |> 
  summarize(mean_ssm = mean(ssm, na.rm = TRUE), 
            sd_ssm = sd(ssm, na.rm = TRUE))

gay_updated2


```

The difference in means for the same-sex marriage script by gay canvassers versus the no contact group is -0.099874. Because this difference is .08 larger than the difference for the wave 1 group, this indicates that there is likely larger differences in people's ssm, however, this is a very small difference. Even a mere .09 difference does not really have a large impact on someone's ssm, so these groups are also likely similar at baseline.
